A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-06-17 paper/paper.Rnw

\paragraph{Model Predictions}
\mt{The ROC curves provide only a general summary of model accuracy; to learn more about how specific images are classified, we can view images from the test set along with their respective nine model predictions.} \autoref{fig:single-exemplars} shows model predictions for images that contain only one type of shape, and \autoref{fig:multi-exemplars} shows predictions for images containing multiple shapes. Most predictions for the single-class images are \fix{promising}; there are some confusions between circle/text and polygon/quad, but all of the true shapes are corectly identified by the model. \fix{The multi-label images also perform quite well; again, true labels are almost all present, with a small number of false positive labels. [Expand on specific cases more, once determining how many examples to keep and how much to highlight errors.] A later section will discuss possible causes for these class confusions.}

@@

\fix{Figures \ref{fig:single-exemplars} and \ref{multi-exemplars} provide representative examples of classifications across multiple categories; it is also useful to examine many cases within a given shape.} \mt{\autoref{fig:chevrons-consistency} shows a number of images containing chevrons. The top four rows show regularly repeating chevron patterns and seems to indicate that the model optimally identifies chevrons of a certain width; wide chevrons cross into the realm of bowties, whereas narrow chevrons become indistinguishable from lines. The next six rows show individual and closed chevrons. There is a significant amount of confusion between these wider chevrons and quadrilaterals. Finally, the bottom four rows show less-than-standard chevrons. The rounded chevron has a much lower prediction than those with sharper angles, but still exceeds the EER for chevron; the white chevrons are confounded with overlaid circles, which introduces a complexity that the model attributes to text.}

>>>>

\paragraph{Model Predictions}
The ROC curves provide only a general summary of model accuracy; to learn more about how specific images are classified, we can view images from the test set along with their respective nine model predictions. \autoref{fig:single-exemplars} shows model predictions for images that contain only one type of shape, and \autoref{fig:multi-exemplars} shows predictions for images containing multiple shapes. Most predictions for the single-class images are \fix{promising}; there are some confusions between circle/text and polygon/quad, but all of the true shapes are corectly identified by the model. \fix{The multi-label images also perform quite well; again, true labels are almost all present, with a small number of false positive labels. [Expand on specific cases more, once determining how many examples to keep and how much to highlight errors.] A later section will discuss possible causes for these class confusions.}

@@

\fix{Figures \ref{fig:single-exemplars} and \ref{multi-exemplars} provide representative examples of classifications across multiple categories; it is also useful to examine many cases within a given shape.} \autoref{fig:chevrons-consistency} shows a number of images containing chevrons. The top four rows show regularly repeating chevron patterns and seems to indicate that the model optimally identifies chevrons of a certain width; wide chevrons cross into the realm of bowties, whereas narrow chevrons become indistinguishable from lines. The next six rows show individual and closed chevrons. There is a significant amount of confusion between these wider chevrons and quadrilaterals. Finally, the bottom four rows show less-than-standard chevrons. The rounded chevron has a much lower prediction than those with sharper angles, but still exceeds the EER for chevron; the white chevrons are confounded with overlaid circles, which introduces a complexity that the model attributes to text.
